---
title: "Near Analysis Low Fertilizer Removed"
author: "JD Stewart"
date: "2/22/2021"
output: html_document
---

```{r Introduction, echo=FALSE}

# This document contains code for identifying the relationship between spatial distance and crop yields  to determine the extent GCO escape effects are driven by spatial processes. 

# Reproducibility

#This document can be regenerated using Rmarkdown and the associated R-script (Analyses_Figures.R). This R-script, in combination with the supplementary data files (available online at github.com/thecrobe) also allows for full reproducibility of all the the figures and analyses conducted in R. All other analyses are conducted in A`rcMap by ESRI. 
```

# Near Analysis Models 

<div class = "col-md-4">
<br><br> **What Was Tested:** Do crop yields increase from GCOs globally as a function of distance when high fertilizer countries are removed? Note that high fertilizer countries were identified as the top 3 applications of N + P + K bt sum. 
</div>

<div class = "col-md-4">
<br><br> **What This Allows Me To Do:** Identify if yield-distance relationships (near analysis) are a function of evolutionary escape or other fertilizer.
</div>

<div class = "col-md-4">
<br><br> **What Are The Model Assumptions:** GLS models are used as they have less assumptions about error structure and heteroscadicity. 
</div>

```{r,  message=TRUE, warning=FALSE, cache=TRUE, message=FALSE,echo=FALSE}
library(rgdal)
library(maptools)
library(rgeos)
library(ggplot2)
library(dplyr)
library(reshape2)

#ggplot graphic parameters
theme_justin<-theme_bw() +theme(axis.line = element_line(colour = "black"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank())

```


