
---
title: "GCO Crop Pathogens"
author: "JD Stewart (@thecrobe)"
output:
  html_document: default
  pdf_document: default
editor_options:
  chunk_output_type: inline
---

```{r Introduction, echo=FALSE}

# The goal of this study is to answer:

#"Are crop yields greater inside or outside the crop's geographic center of origin as a function of escaping pest and pathogen pressure?"

# Reproducibility

#This document can be regenerated using Rmarkdown and the associated R-script (Analyses_Figures.R). This R-script, in combination with the supplementary data files (available online at github.com/thecrobe) also allows for full reproducibility of all the the figures and analyses conducted in R. All other analyses are conducted in ArcMap by ESRI. 

## Focal Crops (n=12) Barley, Cassava, Groundnuts, Maize, Millet, Rapeseed, Rice, Rye, Sorghum, Soybean, Sunflower, Wheat
  
## Data Sources:
### Crop Yields:
#Resolution: Five minute by five minute (~10km x 10km at equator)) 
  
#Data is extracted from EarthStat for average yields per hectare from 1997-2003 as raster images and then the mean value per country is then calculated using zonal statistics. Data is derived from United Nations Food and Agriculture Organization (FAO), the International Food Policy Research Institute (IFPRI), the Center for Sustainability and the Global Environment (SAGE). When subnational statistics were unavailable, national figures from the Food and Agriculture Organization’s statistical database were used. List of all sources is available on EarthStat 


### Inputs

#Fertilizer 
#Resolution: Five minute by five minute (~10km x 10km at equator)) 
  
#List of all sources is available on EarthStat.A major source of data was the fifth edition of “Fertilizer Use by Crop” (the FUBC5 dataset), a joint publication from the International Fertilizer Industry Association (IFA), the International Fertilizer Development Center (IFDC), the International Potash Institute (IPI), the Phosphate and Potash Institute (PPI), and the Food and Agriculture Organization of the United Nations (FAO). 

#The publication contains national-level application rate data by crop for 42 countries, compiled from the following data sources: FAO questionnaires given to member countries; IFA questionnaires given to industry companies, research institutes, and fertilizer associations; IFDC questionnaires sent to experts attending courses, seminars, and professional meetings; and IPI and PPI communications with experts. Most of the application rate data from the FUBC5 dataset are for the years 1999 or 2000, but data for some countries are as old as 1994 and as recent as 2001. 

## Drivers to test
  
### Climate: 
#Resolution: ~4-km (1/24th degree) spatial resolution averaged across 1997-2003. 
#TerraClimate uses climatically aided interpolation, combining high-spatial resolution climatological normals from the WorldClim dataset, with coarser spatial resolution, but time-varying data from CRU Ts4.0 and the Japanese 55-year Reanalysis (JRA55). 

#### Pests: 
#Resolution: Resolution: Country level. Mean from 1997-2003 derived from FAO

### GDP: 
#Resolution: Country level. Mean from 1997-2003 derived from WorldBank

## Geographic Centers of Origin: 
###These are defined at the country level for each crop with regions being taken from FAOSTAT labels and publications of origins from a mixture of molecular and archaeological studies.
  
### Near East
#  * Barley
#  * Wheat
    
### South America
#  * Cassava
#  * Groundnuts

### Central America 
#  * Maize
    
### China + SE Asia + India
#  * Rice
  
### China
#  * Soybean
#  * Millet
  
### North America 
#  * Sunflower

### North East Africa
#  * Sorghum

### Central Asia, Turkey, Transcaucasia,and Iran  
#  * Rye
  
### Central Europe 
#  * Rapeseed
  
```


```{r Packages, include=TRUE, echo=FALSE, message=FALSE, eval=TRUE, warning=FALSE}


#models
library(wPerm)
library(caret)
library(wPerm)
#library(spatialEco)
#library(rgdal)
library(RVAideMemoire)

#plots
library(RColorBrewer)
library(ggplot2)
library(wesanderson)

#data wrangling
library(reshape2)
library(dplyr)
library(Hmisc)
```

## Boxplots: Inside-Outside GCO

<div class = "col-md-4">
<br><br> **What Was Tested:** Do crop yields vary inside and outside GCO? How do they vary across distance?
</div>

<div class = "col-md-4">
<br><br> **What This Allows Me To Do:** Identify the distribution of yields inside and outside GCO and if they statistically differ.
</div>

<div class = "col-md-4">
<br><br> **What Are The Model Assumptions:** Permutations T-Tests were used to test if there is a significant difference in the means of each crop separated by inside/outside GCO. These tests were chosen as they have few assumptions about the distribution and independence of the data (i.e. exchangability is th only assumption however there is no way to test for this as we do not know the true distribution). Likewise permutational tests destroy the spatial-autocorrelation structure that influences test results. Plots are solely visual. 
</div>

<div class = "col-md-12">
<br><br> **What Are The Model Assumptions:** Permutations T-Tests were used to test if there is a significant difference in the means of each crop separated by inside/outside GCO. These tests were chosen as they have few assumptions about the distribution and independence of the data (i.e. exchangability is th only assumption however there is no way to test for this as we do not know the true distribution). Likewise permutational tests destroy the spatial-autocorrelation structure that influences test results. Plots are solely visual.


</div>


```{r Boxplots, Merge Mapping,echo=FALSE,warning=FALSE}
mapping<-read.csv("Fishnets/mapping_GCOfishnet.csv", header=T, fileEncoding = "UTF-8-BOM")
yield<-read.csv("Fishnets/yield_fishnet.csv", header=T)

#colors
sighigh<-"#00ADB6"
siglow<-"#FFA800"
insig<-"#38474E"

yield.mapping<-merge(mapping,yield)

# Barley 
barley<-na.omit(yield.mapping %>% dplyr::select(barley_HgHa,barley_GCO))

#Inside vs Outside GCO 
barley.inside<-filter(barley, barley_GCO == "Inside")
barley.outside<-filter(barley, barley_GCO == "Outside")
barley.m<-melt(barley)
summary(barley.inside)
summary(barley.outside)

# Permutational T Test
set.seed(8675309)
barley.perm<-perm.t.test(barley.inside$barley_HgHa,barley.outside$barley_HgHa,progress=FALSE)
print(barley.perm)

#Plot
ggplot(barley.m, aes(x=barley.m$barley_GCO, y=barley.m$value)) + 
  geom_boxplot(fill=sighigh, fill="transparent", width=0.4)+
  theme_bw() +
  theme(axis.line = element_line(colour = "black"),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.border = element_blank(),
    panel.background = element_blank()) + 
  ylab("Yield (Hg/Ha)") +xlab("") + labs(color='GCO') 


# Cassava 
cassava<-na.omit(yield.mapping %>% dplyr::select(cassava_HgHa,cassava_GCO))

#Outlier removal
hist(cassava$cassava_HgHa)
qqnorm(cassava$cassava_HgHa)
cassava.filter<-cassava %>% filter(between(cassava_HgHa, quantile(cassava_HgHa, .01), quantile(cassava_HgHa, .99))) #remove top and bottom 1% 
hist(cassava.filter$cassava_HgHa)
qqnorm(cassava.filter$cassava_HgHa)
dim(cassava) - dim(cassava.filter) # Num Outliers Removed
summary(cassava.filter)
cassava<-cassava.filter


#Inside vs Outside GCO 
cassava.inside<-filter(cassava, cassava_GCO == "Inside")
cassava.outside<-filter(cassava, cassava_GCO == "Outside")
cassava.m<-melt(cassava)
summary(cassava.inside)
summary(cassava.outside)

# Permutational T Test
set.seed(12345)
cassava.perm<-perm.t.test(cassava.inside$cassava_HgHa,cassava.outside$cassava_HgHa,progress=FALSE)
print(cassava.perm)

#Plot
ggplot(cassava.m, aes(x=cassava.m$cassava_GCO, y=cassava.m$value)) +  geom_boxplot(fill=sighigh, fill="transparent", width=0.4)+
  theme_bw() +
  theme(axis.line = element_line(colour = "black"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank()) + 
  ylab("Yield (Hg/Ha)") +xlab("") + labs(color='GCO') 



## Groundnut 
groundnut<-na.omit(yield.mapping %>% dplyr::select(groundnut_HgHa,groundnut_GCO))
#Outlier removal
hist(groundnut$groundnut_HgHa)
qqnorm(groundnut$groundnut_HgHa)
groundnut.filter<-groundnut %>% filter(between(groundnut_HgHa, quantile(groundnut_HgHa, .01), quantile(groundnut_HgHa, .99))) #remove top and bottom 1% 
hist(groundnut.filter$groundnut_HgHa)
qqnorm(groundnut.filter$groundnut_HgHa)
dim(groundnut) - dim(groundnut.filter) # Num Outliers Removed
summary(groundnut.filter)
groundnut<-groundnut.filter


#Inside vs Outside GCO 
groundnut.inside<-filter(groundnut, groundnut_GCO == "Inside")
groundnut.outside<-filter(groundnut, groundnut_GCO == "Outside")
groundnut.m<-melt(groundnut)
summary(groundnut.inside)
summary(groundnut.outside)

# Permutational T Test
set.seed(8675309)
groundnut.perm<-perm.t.test(groundnut.inside$groundnut_HgHa,groundnut.outside$groundnut_HgHa, progress=FALSE)
print(groundnut.perm)

#Plot
ggplot(groundnut.m, aes(x=groundnut.m$groundnut_GCO, y=groundnut.m$value)) +  geom_boxplot(fill=sighigh, fill="transparent", width=0.4)+
  theme_bw() +
  theme(axis.line = element_line(colour = "black"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank()) + 
  ylab("Yield (Hg/Ha)") +xlab("") + labs(color='GCO') 


## Maize 
maize<-na.omit(yield.mapping %>% dplyr::select(maize_HgHa,maize_GCO))

#Outlier removal
hist(maize$maize_HgHa)
qqnorm(maize$maize_HgHa)
maize.filter<-maize %>% filter(between(maize_HgHa, quantile(maize_HgHa, .01), quantile(maize_HgHa, .99))) #remove top and bottom 1% 
hist(maize.filter$maize_HgHa)
qqnorm(maize.filter$maize_HgHa)
dim(maize) - dim(maize.filter) # Num Outliers Removed
summary(maize.filter)
maize<-maize.filter
 

#Inside vs Outside GCO 
maize.inside<-filter(maize, maize_GCO == "Inside")
maize.outside<-filter(maize, maize_GCO == "Outside")
maize.m<-melt(maize)
summary(maize.inside)
summary(maize.outside)

# Permutational T Test
set.seed(8675309)
maize.perm<-perm.t.test(maize.inside$maize_HgHa,maize.outside$maize_HgHa, progress=FALSE)
print(maize.perm)

#Plot
ggplot(maize.m, aes(x=maize.m$maize_GCO, y=maize.m$value)) +  geom_boxplot(fill="#B9BEBE", fill="transparent", width=0.4)+
  theme_bw() +
  theme(axis.line = element_line(colour = "black"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank()) + 
  ylab("Yield (Hg/Ha)") +xlab("") + labs(color='GCO') 

## Millet 
millet<-na.omit(yield.mapping %>% dplyr::select(millet_HgHa,millet_GCO))

#Outlier removal
hist(millet$millet_HgHa)
qqnorm(millet$millet_HgHa)
millet.filter<-millet %>% filter(between(millet_HgHa, quantile(millet_HgHa, .01), quantile(millet_HgHa, .99))) #remove top and bottom 1% 
hist(millet.filter$millet_HgHa)
qqnorm(millet.filter$millet_HgHa)
dim(millet) - dim(millet.filter) # Num Outliers Removed
summary(millet.filter)
millet<-millet.filter


#Inside vs Outside GCO 
millet.inside<-filter(millet, millet_GCO == "Inside")
millet.outside<-filter(millet, millet_GCO == "Outside")
millet.m<-melt(millet)
summary(millet.inside)
summary(millet.outside)

# Permutational T Test
set.seed(8675309)
millet.perm<-perm.t.test(millet.inside$millet_HgHa,millet.outside$millet_HgHa, progress=FALSE)
print(millet.perm)

#Plot
ggplot(millet.m, aes(x=millet.m$millet_GCO, y=millet.m$value)) +  geom_boxplot(fill=siglow, fill="transparent", width=0.4)+
  theme_bw() +
  theme(axis.line = element_line(colour = "black"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank()) + 
  ylab("Yield (Hg/Ha)") +xlab("") + labs(color='GCO') 


# Permutational T Test
set.seed(8675309)
millet.perm<-perm.t.test(millet.inside$millet_HgHa,millet.outside$millet_HgHa, progress=FALSE)
print(millet.perm)

## Rapeseed 
rapeseed<-na.omit(yield.mapping %>% dplyr::select(rapeseed_HgHa,rapeseed_GCO))

#Outlier removal
hist(rapeseed$rapeseed_HgHa)
qqnorm(rapeseed$rapeseed_HgHa)
rapeseed.filter<-rapeseed %>% filter(between(rapeseed_HgHa, quantile(rapeseed_HgHa, .01), quantile(rapeseed_HgHa, .99))) #remove top and bottom 1% 
hist(rapeseed.filter$rapeseed_HgHa)
qqnorm(rapeseed.filter$rapeseed_HgHa)
dim(rapeseed) - dim(rapeseed.filter) # Num Outliers Removed
summary(rapeseed.filter)
rapeseed<-rapeseed.filter


#Inside vs Outside GCO 
rapeseed.inside<-filter(rapeseed, rapeseed_GCO == "Inside")
rapeseed.outside<-filter(rapeseed, rapeseed_GCO == "Outside")
rapeseed.m<-melt(rapeseed)
summary(rapeseed.inside)
summary(rapeseed.outside)

# Permutational T Test
set.seed(8675309)
rapeseed.perm<-perm.t.test(rapeseed.inside$rapeseed_HgHa,rapeseed.outside$rapeseed_HgHa, progress=FALSE)
print(rapeseed.perm)

#Plot
ggplot(rapeseed.m, aes(x=rapeseed.m$rapeseed_GCO, y=rapeseed.m$value)) +  geom_boxplot(fill=siglow, fill="transparent", width=0.4)+
  theme_bw() +
  theme(axis.line = element_line(colour = "black"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank()) + 
  ylab("Yield (Hg/Ha)") +xlab("") + labs(color='GCO') 


## Rice 
rice<-na.omit(yield.mapping %>% dplyr::select(rice_HgHa,rice_GCO))

#Outlier removal
hist(rice$rice_HgHa)
qqnorm(rice$rice_HgHa)
rice.filter<-rice %>% filter(between(rice_HgHa, quantile(rice_HgHa, .01), quantile(rice_HgHa, .99))) #remove top and bottom 1% 
hist(rice.filter$rice_HgHa)
qqnorm(rice.filter$rice_HgHa)
dim(rice) - dim(rice.filter) # Num Outliers Removed
summary(rice.filter)
rice<-rice.filter


#Filter
rice.inside<-filter(rice, rice_GCO == "Inside")
rice.outside<-filter(rice, rice_GCO == "Outside")
rice.m<-melt(rice)
summary(rice.inside)
summary(rice.outside)

# Permutational T Test
set.seed(8675309)
rice.perm<-perm.t.test(rice.inside$rice_HgHa,rice.outside$rice_HgHa, progress=FALSE)
print(rice.perm)

#Plot
ggplot(rice.m, aes(x=rice.m$rice_GCO, y=rice.m$value)) +  geom_boxplot(fill=siglow, fill="transparent", width=0.4)+
  theme_bw() +
  theme(axis.line = element_line(colour = "black"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank()) + 
  ylab("Yield (Hg/Ha)") +xlab("") + labs(color='GCO') 


## Rye 
rye<-na.omit(yield.mapping %>% dplyr::select(rye_HgHa,rye_GCO))

#Outlier removal
hist(rye$rye_HgHa)
qqnorm(rye$rye_HgHa)
rye.filter<-rye %>% filter(between(rye_HgHa, quantile(rye_HgHa, .01), quantile(rye_HgHa, .99))) #remove top and bottom 1% 
hist(rye.filter$rye_HgHa)
qqnorm(rye.filter$rye_HgHa)
dim(rye) - dim(rye.filter) # Num Outliers Removed
summary(rye.filter)
rye<-rye.filter


#Inside vs Outside GCO 
rye.inside<-filter(rye, rye_GCO == "Inside")
rye.outside<-filter(rye, rye_GCO == "Outside")
rye.m<-melt(rye)
summary(rye.inside)
summary(rye.outside)

# Permutational T Test
set.seed(8675309)
rye.perm<-perm.t.test(rye.inside$rye_HgHa,rye.outside$rye_HgHa,progress=FALSE)
print(rye.perm)


#Plot
ggplot(rye.m, aes(x=rye.m$rye_GCO, y=rye.m$value)) +  geom_boxplot(fill=sighigh, fill="transparent", width=0.4)+
  theme_bw() +
  theme(axis.line = element_line(colour = "black"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank()) + 
  ylab("Yield (Hg/Ha)") +xlab("") + labs(color='GCO') 


## Sorghum 
sorghum<-na.omit(yield.mapping %>% dplyr::select(sorghum_HgHa,sorghum_GCO))

#Outlier removal
hist(sorghum$sorghum_HgHa)
qqnorm(sorghum$sorghum_HgHa)
sorghum.filter<-sorghum %>% filter(between(sorghum_HgHa, quantile(sorghum_HgHa, .01), quantile(sorghum_HgHa, .99))) #remove top and bottom 1% 
hist(sorghum$sorghum_HgHa)
qqnorm(sorghum$sorghum_HgHa)
dim(sorghum) - dim(sorghum.filter) # Num Outliers Removed
summary(sorghum.filter)
sorghum<-sorghum.filter

#Inside vs Outside GCO 
sorghum.inside<-filter(sorghum, sorghum_GCO == "Inside")
sorghum.outside<-filter(sorghum, sorghum_GCO == "Outside")
sorghum.m<-melt(sorghum)
summary(sorghum.inside)
summary(sorghum.outside)

# Permutational T Test
set.seed(12345)
sorghum.perm<-perm.t.test(sorghum.inside$sorghum_HgHa,sorghum.outside$sorghum_HgHa, progress=FALSE)
print(sorghum.perm)

#Plot
ggplot(sorghum.m, aes(x=sorghum.m$sorghum_GCO, y=sorghum.m$value)) +  geom_boxplot(fill=sighigh, fill="transparent", width=0.4)+
  theme_bw() +
  theme(axis.line = element_line(colour = "black"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank()) + 
  ylab("Yield (Hg/Ha)") +xlab("") + labs(color='GCO') 



## Soybean 
soybean<-na.omit(yield.mapping %>% dplyr::select(soybean_HgHa,soybean_GCO))

#Outlier Removal
hist(soybean$soybean_HgHa)
qqnorm(soybean$soybean_HgHa)
soybean.filter<-soybean %>% filter(between(soybean_HgHa, quantile(soybean_HgHa, .01), quantile(soybean_HgHa, .99))) #remove top and bottom 1% 
hist(soybean.filter$soybean_HgHa)
qqnorm(soybean.filter$soybean_HgHa)
dim(soybean) - dim(soybean.filter) # Num Outliers Removed
summary(soybean)
summary(soybean.filter)
soybean<-soybean.filter



#Inside vs Outside GCO 
soybean.inside<-filter(soybean, soybean_GCO == "Inside")
soybean.outside<-filter(soybean, soybean_GCO == "Outside")
soybean.m<-melt(soybean)
summary(soybean.inside)
summary(soybean.outside)

# Permutational T Test
set.seed(8675309)
soybean.perm<-perm.t.test(soybean.inside$soybean_HgHa,soybean.outside$soybean_HgHa, progress=FALSE)
print(soybean.perm)

#Plot
ggplot(soybean.m, aes(x=soybean.m$soybean_GCO, y=soybean.m$value)) +  geom_boxplot(fill=siglow, fill="transparent", width=0.4)+
  theme_bw() +
  theme(axis.line = element_line(colour = "black"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank()) + 
  ylab("Yield (Hg/Ha)") +xlab("") + labs(color='GCO') 


## Sunflower 
sunflower<-na.omit(yield.mapping %>% dplyr::select(sunflower_HgHa,sunflower_GCO))

#Outlier Removal
hist(sunflower$sunflower_HgHa)
qqnorm(sunflower$sunflower_HgHa)
sunflower.filter<-sunflower %>% filter(between(sunflower_HgHa, quantile(sunflower_HgHa, .01), quantile(sunflower_HgHa, .99))) #remove top and bottom 1% 
hist(sunflower.filter$sunflower_HgHa)
qqnorm(sunflower.filter$sunflower_HgHa)
dim(sunflower) - dim(sunflower.filter) # Num Outliers Removed
summary(sunflower)
summary(sunflower.filter)
sunflower<-sunflower.filter


#Inside vs Outside GCO 
sunflower.inside<-filter(sunflower, sunflower_GCO == "Inside")
sunflower.outside<-filter(sunflower, sunflower_GCO == "Outside")
sunflower.m<-melt(sunflower)
summary(sunflower.inside)
summary(sunflower.outside)

# Permutational T Test
sunflower.perm<-perm.t.test(sunflower.inside$sunflower_HgHa,sunflower.outside$sunflower_HgHa, progress=FALSE)
print(sunflower.perm)

#Plot
ggplot(sunflower.m, aes(x=sunflower.m$sunflower_GCO, y=sunflower.m$value, color=sunflower.m$sunflower_GCO)) + 
  geom_jitter(alpha=0.4, width=0.2) + 
  geom_boxplot(color="black", fill="transparent", width=0.4)+
  scale_color_manual(values = wes_palette("Darjeeling1",type = "discrete")) + 
  theme_bw() +
  theme(axis.line = element_line(colour = "black"),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.border = element_blank(),
    panel.background = element_blank()) + 
  ylab("Yield (Hg/Ha)") +xlab("") + labs(color='GCO') 


## Wheat 
wheat<-na.omit(yield.mapping %>% dplyr::select(wheat_HgHa,wheat_GCO))

#Outlier Removal
hist(wheat$wheat_HgHa)
qqnorm(wheat$wheat_HgHa)
wheat.filter<-wheat %>% filter(between(wheat_HgHa, quantile(wheat_HgHa, .01), quantile(wheat_HgHa, .99))) #remove top and bottom 1% 
hist(wheat.filter$wheat_HgHa)
qqnorm(wheat.filter$wheat_HgHa)
dim(wheat) - dim(wheat.filter) # Num Outliers Removed
summary(wheat)
summary(wheat.filter)
wheat<-wheat.filter


#Inside vs Outside GCO 
wheat.inside<-filter(wheat, wheat_GCO == "Inside")
wheat.outside<-filter(wheat, wheat_GCO == "Outside")
wheat.m<-melt(wheat)
summary(wheat.inside)
summary(wheat.outside)

# Permutational T Test
wheat.perm<-perm.t.test(wheat.inside$wheat_HgHa,wheat.outside$wheat_HgHa, progress=FALSE)
print(wheat.perm)

#Plot
ggplot(wheat.m, aes(x=wheat.m$wheat_GCO, y=wheat.m$value, color=wheat.m$wheat_GCO)) + 
  geom_jitter(alpha=0.4, width=0.2) + 
  geom_boxplot(color="black", fill="transparent", width=0.4)+
  scale_color_manual(values = wes_palette("Darjeeling1",type = "discrete")) + 
  theme_bw() +
  theme(axis.line = element_line(colour = "black"),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.border = element_blank(),
    panel.background = element_blank()) + 
  ylab("Yield (Hg/Ha)") +xlab("") + labs(color='GCO') 

```

## Near Analysis 

<div class = "col-md-4">
<br><br> **What Was Tested:** Does a distance decay relationship exist for each crop as you increase distance from GCO? If this is true, what is the magnitude and direction? 
</div>

<div class = "col-md-4">
<br><br> **What This Allows Me To Do:** Identify if crop yields are greater as a fucntion of distance from GCO
</div>

<div class = "col-md-4">
<br><br> **What Are The Model Assumptions:**For generating the near table (a table of the distance centroid of each pixel outside of the GCO and crop yield) a geodesic approach was used to be more accurate at the equator and the poles. Likewise, permutational
</div>

 
```{r Near Analysis, message=TRUE, warning=FALSE, cache=TRUE}

### Barley ###
barley.near<-read.csv(file = "Near_All/Barley_Near_Centroid.csv", header=T)

#Outlier Removal
barley.filter<-barley.near %>% filter(between(mean_barle, quantile(mean_barle, .01), quantile(mean_barle, .99))) #remove top and bottom 1% 
barley.near<-barley.filter
summary(barley.near)
#Permutational  Correlation
 
cor.test(x = log10(barley.near$mean_barle),log10(barley.near$NEAR_DIST),method = "pearson")


#Plot
ggplot(barley.near, aes(x=log10(NEAR_DIST), y=log10(mean_barle))) +
  geom_point(alpha=0.1, color="#00A9B4") + geom_smooth(method = "loess",color="#DB3500") + theme_bw() +
  theme(axis.line = element_line(colour = "black"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank()) + 
  ylab("Log10 Yield (Hg/Ha)") +xlab("Log 10 Distance") + labs(color='GCO')


### Cassava ###
cassava.near<-read.csv(file = "Near_All/Cassava_Near_Centroid.csv", header=T)

#Outlier Removal
cassava.filter<-cassava.near %>% filter(between(mean_cassa, quantile(mean_cassa, .01), quantile(mean_cassa, .99))) #remove top and bottom 1% 
cassava.near<-cassava.filter

#Permutational  Correlartion
cor.test(log10(cassava.near$NEAR_DIST+1), log10(cassava.near$mean_cassa), method = "pearson")

#Plot
ggplot(cassava.near, aes(x=log10(NEAR_DIST), y=log10(cassava.near$mean_cassa))) +
  geom_point(alpha=0.2, color="#00A9B4") + geom_smooth(method = "lm",color="#DB3500") +
  theme_bw() +
  theme(axis.line = element_line(colour = "black"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank()) + 
  ylab("Log10 Yield (Hg/Ha)") +xlab("Log 10 Distance") + labs(color='GCO')


### Groundnut ###
groundnut.near<-read.csv(file = "Near_All/Groundnut_Near_Centroid.csv", header=T)

#Outlier Removal
groundnut.filter<-groundnut.near %>% filter(between(mean_groun, quantile(mean_groun, .01), quantile(mean_groun, .99))) #remove top and bottom 1% 
groundnut.near<-groundnut.filter

#Correlartion

cor.test(log10(groundnut.near$NEAR_DIST+1),log10(groundnut.near$mean_groun))

#Plot
ggplot(groundnut.near, aes(x=log10(NEAR_DIST), y=log10(groundnut.near$mean_groun))) +
  geom_point(alpha=0.2, color="#00A9B4") + geom_smooth(method = "lm",color="#DB3500") +
  theme_bw() +
  theme(axis.line = element_line(colour = "black"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank()) + 
  ylab("Log10 Yield (Hg/Ha)") +xlab("Log 10 Distance") + labs(color='GCO')

### Maize ###
maize.near<-read.csv(file = "Near_All/Maize_Near_Centroid.csv", header=T)

#Outlier Removal
maize.filter<-maize.near %>% filter(between(mean_maize, quantile(mean_maize, .01), quantile(mean_maize, .99))) #remove top and bottom 1% 
maize.near<-maize.filter

#Permutational  Correlation
cor.test(x = log10(maize.near$NEAR_DIST+1),maize.near$mean_maize,method = "pearson")

#Plot
ggplot(maize.near, aes(x=log10(NEAR_DIST), y=log10(maize.near$mean_maize))) +
  geom_point(alpha=0.2, color="#F0AB00") +geom_smooth(method = "lm",color="#DB3500") +
  theme_bw() +
  theme(axis.line = element_line(colour = "black"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank()) + 
  ylab("Log10 Yield (Hg/Ha)") +xlab("Log 10 Distance") + labs(color='GCO')

### Millet ###
millet.near<-read.csv(file = "Near_All/Millet_Near_Centroid.csv", header=T)

#Outlier Removal
millet.filter<-millet.near %>% filter(between(mean_mille, quantile(mean_mille, .01), quantile(mean_mille, .99))) #remove top and bottom 1% 
millet.near<-millet.filter

#Permutational  Correlation
cor.test(x = log10(millet.near$NEAR_DIST+1),millet.near$mean_mille,method = "pearson")

#Plot
ggplot(millet.near, aes(x=log10(NEAR_DIST), y=log10(millet.near$mean_mille))) +
  geom_point(alpha=0.2, color="#FFB100") + geom_smooth(method = "lm",color="#DB3500") +
  theme_bw() +
  theme(axis.line = element_line(colour = "black"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank()) + 
  ylab("Log10 Yield (Hg/Ha)") +xlab("Log 10 Distance") + labs(color='GCO')


### Rapeseed ###
rapeseed.near<-read.csv(file = "Near_All/Rapeseed_Near_Centroid.csv", header=T)

#Outlier Removal
rapeseed.filter<-rapeseed.near %>% filter(between(mean_rapes, quantile(mean_rapes, .01), quantile(mean_rapes, .99))) #remove top and bottom 1% 
rapeseed.near<-rapeseed.filter

#Permutational  Correlartion
cor.test(x = log10(rapeseed.near$NEAR_DIST+1),rapeseed.near$mean_rapes,method = "pearson")

ggplot(rapeseed.near, aes(x=log10(NEAR_DIST), y=log10(rapeseed.near$mean_rapes))) +
  geom_point(alpha=0.2, color="#FFAF02") + geom_smooth(method = "lm",color="#DB3500") +
  theme_bw() +
  theme(axis.line = element_line(colour = "black"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank()) + 
  ylab("Log10 Yield (Hg/Ha)") +xlab("Log 10 Distance") + labs(color='GCO')

### Rice ###
rice.near<-read.csv(file = "Near_All/Rice_Near_Centroid.csv", header=T)

#Outlier Removal
rice.filter<-rice.near %>% filter(between(mean_rice, quantile(mean_rice, .01), quantile(mean_rice, .99))) #remove top and bottom 1% 
rice.near<-rice.filter
#Permutational  Correlation

cor.test(x = log10(rice.near$NEAR_DIST+1),rice.near$mean_rice,method = "pearson")

#Plot
ggplot(rice.near, aes(x=log10(NEAR_DIST), y=log10(rice.near$mean_rice))) +
  geom_point(alpha=0.2, color="#FBA900") + geom_smooth(method = "lm",color="#DB3500") +
  theme_bw() +
  theme(axis.line = element_line(colour = "black"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank()) + 
  ylab("Log10 Yield (Hg/Ha)") +xlab("Log 10 Distance") + labs(color='GCO')

### Rye ###
rye.near<-read.csv(file = "Near_All/Rye_Near_Centroid.csv", header=T)

#Outlier Removal
rye.filter<-rye.near %>% filter(between(mean_rye_Y, quantile(mean_rye_Y, .01), quantile(mean_rye_Y, .99))) #remove top and bottom 1% 
rye.near<-rye.filter

#Permutational  Correlation
cor.test(x = log10(rye.near$NEAR_DIST+1),rye.near$mean_rye_Y,method = "pearson")

#Plot
ggplot(rye.near, aes(x=log10(NEAR_DIST), y=log10(rye.near$mean_rye_Y))) +
  geom_point(alpha=0.2, color="#FFB200") +geom_smooth(method = "lm",color="#DB3500") +
  theme_bw() +
  theme(axis.line = element_line(colour = "black"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank()) + 
  ylab("Log10 Yield (Hg/Ha)") +xlab("Log 10 Distance") + labs(color='GCO')

### Sorghum ###
sorghum.near<-read.csv(file = "Near_All/Sorghum_Near_Centroid.csv", header=T)

#Outlier Removal
sorghum.filter<-sorghum.near %>% filter(between(mean_sorgh, quantile(mean_sorgh, .01), quantile(mean_sorgh, .99))) #remove top and bottom 1% 
sorghum.near<-sorghum.filter

#Permutational  Correlartion
cor.test(x = log10(sorghum.near$NEAR_DIST+1),sorghum.near$mean_sorgh,method = "pearson")

#Plot
ggplot(sorghum.near, aes(x=log10(NEAR_DIST), y=log10(sorghum.near$mean_sorgh))) +
     geom_point(alpha=0.2, color="#00A9B4") +geom_smooth(method = "lm",color="#DB3500") + theme_bw() +theme(axis.line = element_line(colour = "black"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank()) + 
  ylab("Log10 Yield (Hg/Ha)") +xlab("Log 10 Distance") + labs(color='GCO')

### Soybean ###
soybean.near<-read.csv(file = "Near_All/Soybean_Near_Centroid.csv", header=T)

#Outlier Removal
soybean.filter<-soybean.near %>% filter(between(mean_soybe, quantile(mean_soybe, .01), quantile(mean_soybe, .99))) #remove top and bottom 1% 
soybean.near<-soybean.filter

#Permutational  Correlation
cor.test(x = log10(soybean.near$NEAR_DIST+1),soybean.near$mean_soybe,method = "pearson")

#Plot
ggplot(soybean.near, aes(x=log10(NEAR_DIST), y=log10(soybean.near$mean_soybe))) +
  geom_point(alpha=0.2, color="#00A9B4") +geom_smooth(method = "lm",color="#DB3500") +
  theme_bw() +
  theme(axis.line = element_line(colour = "black"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank()) + 
  ylab("Log10 Yield (Hg/Ha)") +xlab("Log 10 Distance") + labs(color='GCO')

### Sunflower ###
sunflower.near<-read.csv(file = "Near_All/Sunflower_Near_Centroid.csv", header=T)

#Outlier Removal
sunflower.filter<-sunflower.near %>% filter(between(mean_sunfl, quantile(mean_sunfl, .01), quantile(mean_sunfl, .99))) #remove top and bottom 1% 
sunflower.near<-sunflower.filter

#Permutational Spearman Correlation
cor.test(x = log10(sunflower.near$NEAR_DIST+1),sunflower.near$mean_sunfl,method = "pearson")
print(near.sunflower$Observed) #coefficient
print(near.sunflower$P.value) # p-value
#Plot
ggplot(sunflower.near, aes(x=log10(NEAR_DIST), y=log10(sunflower.near$mean_sunfl))) +
  geom_point(alpha=0.2, color="#38474E") + geom_smooth(method = "lm",color="#DB3500") +
  theme_bw() +
  theme(axis.line = element_line(colour = "black"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank()) + 
  ylab("Log10 Yield (Hg/Ha)") +xlab("Log 10 Distance") + labs(color='GCO')


### Wheat ### 
wheat.near<-read.csv(file = "Near_All/Wheat_Near_Centroid.csv", header=T)

#Outlier Removal
wheat.filter<-wheat.near %>% filter(between(mean_wheat, quantile(mean_wheat, .01), quantile(mean_wheat, .99))) #remove top and bottom 1% 
wheat.near<-wheat.filter

#Permutational  Correlartion
cor.test(x = log10(wheat.near$NEAR_DIST+1),wheat.near$mean_wheat,method = "pearson")


#Plot
ggplot(wheat.near, aes(x=log10(NEAR_DIST), y=log10(wheat.near$mean_wheat))) +
  geom_point(alpha=0.2, color="#0BAAB4") + geom_smooth(method = "lm",color="#DB3500") +
  theme_bw() +
  theme(axis.line = element_line(colour = "black"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank()) + 
  ylab("Log10 Yield (Hg/Ha)") +xlab("Log 10 Distance") + labs(color='GCO')


```


 
```{r GLS - Near Analysis, fig.align='center',message=FALSE, warning=FALSE, cache=TRUE}
=======
```{r: GLS - Near Analysis, Variable Direction Estimation - GLS, fig.align='center',message=FALSE, warning=FALSE, cache=TRUE}
 

library(rcompanion)
library(nlme)
library(MASS)



##Barley
barley.near<-read.csv(file = "Near_Coded/Barley_Near.csv", header=T)
summary(barley.near) #check for NAs

plot(density(barley.near$mean_barle)) #check distribution
plot(density(barley.near$NEAR_DIST)) #check distribution

### OLS regression
barley.near.ols<-lm(mean_barle ~ NEAR_DIST,, data = barley.near)
summary(barley.near.ols)
plot(barley.near.ols)
hist(residuals(barley.near.ols))
AIC(barley.near.ols) #AIC = 36206.46


#Barley - Null Model (No Variance Structure)
barley.null<-gls(log10(mean_barle)~ NEAR_DIST, data=barley.near)
summary(barley.null) #AIC = 	6329.558	
plot(barley.null) #plot residuals
hist(residuals(barley.null)) #residual histogram

#Exponential - Log Transformation
barley.near$logYield<-log10(barley.near$mean_barle)
barley.gls.exp.log <- gls(logYield ~ NEAR_DIST,, data = barley.near, weights = varExp())
summary(barley.gls.exp.log) #AIC = 18521.71
plot(barley.gls.exp.log) #plot residuals
hist(residuals(barley.gls.exp.log)) #residual histogram


# Pseud-R2 - Used model with lowest AIC and Best Residual Distribution
barley.r2<-nagelkerke(barley.gls.exp.log, restrictNobs = FALSE)
print(barley.r2)


## Cassava
cassava.near<-read.csv(file = "Near_Coded/Cassava_Near.csv", header=T)
summary(cassava.near) #check for NAs
plot(density(cassava.near$mean_cassa)) #check distribution
plot(density(cassava.near$NEAR_DIST)) #check distribution

### OLS regression
cassava.near.ols<-lm(log10(mean_cassa) ~ NEAR_DIST,, data = cassava.near)
summary(cassava.near.ols)
plot(cassava.near.ols)
hist(residuals(cassava.near.ols))
AIC(cassava.near.ols) #AIC = 6282.759

#Cassava - Null Model (No Variance Structure)
cassava.null<-gls(log10(mean_cassa)~ NEAR_DIST, data=cassava.near)
summary(cassava.null) #AIC = 	6329.558	
plot(cassava.null) #plot residuals
hist(residuals(cassava.gls.exp)) #residual histogram

#Exponential - Log Transformation
cassava.near$logYield<-log10(cassava.near$mean_cassa)
cassava.gls.exp.log <- gls(logYield ~ NEAR_DIST,, data = cassava.near, weights = varExp())
summary(cassava.gls.exp.log) #AIC = 6049.93	
plot(cassava.gls.exp.log) #plot residuals
hist(residuals(cassava.gls.exp.log)) #residual histogram

# Pseud-R2 - Used model with lowest AIC and Best Residual Distribution
library(rcompanion)
cassava.r2<-nagelkerke(cassava.gls.exp.log, restrictNobs = FALSE)
print(cassava.r2)

```


## Variable Direction Estimation

<div class = "col-md-4">
<br><br> **What Was Tested:** How do crop yields increase or decrease with each single explantory variable in the RFR models? 
</div>

<div class = "col-md-4">
<br><br> **What This Allows Me To Do:** Identify how the emergent correlations from RFR are driven by individual variables. 
</div>

<div class = "col-md-4">
<br><br> **What Are The Model Assumptions:** Permutational Spearman rank-order correlations are used as they will identify monotonic relationships.Permutational tests were chosen as they have few assumptions about the distribution and independence of the data (i.e. exchangability is th only assumption however there is no way to test for this as we do not know the true distribution). Likewise permutational tests destroy the spatial-autocorrelation structure that influences test results. Plots are solely visual.
</div>


```{r Variable Direction Estimation,fig.align='center',message=FALSE, warning=FALSE, cache=TRUE}

## Barley
rf.barley<-read.csv(file="Models/Barley_RF.csv", header = T, row.names = 1)
rf.barley<-na.omit(rf.barley)
rf.barley<-log10(rf.barley+1)

#AET
barley.aet<-perm.relation(rf.barley$barley_HgHa,rf.barley$AET_mean,method = "pearson") 
#print(barley.aet)

#GDP
barley.gdp<-perm.relation(rf.barley$barley_HgHa,rf.barley$GDP_Mean,method = "pearson") 
#print(barley.gdp)

#Pest
barley.pest<-perm.relation(rf.barley$barley_HgHa,rf.barley$Pesticide,method = "pearson") 
#print(barley.pest)

#Fertilizer
barley.fert<-perm.relation(rf.barley$barley_HgHa,rf.barley$Barley_Fertilizer,method = "pearson") #print(barley.fert)

##Cassava
rf.cassava<-read.csv(file="Models/Cassava_RF.csv", header = T, row.names = 1)
rf.cassava$Growing_Mean<-as.numeric(rf.cassava$Growing_Mean)
rf.cassava<-na.omit(rf.cassava)
rf.cassava<-log10(rf.cassava+1)

#AET
cassava.aet<-perm.relation(rf.cassava$cassava_HgHa,rf.cassava$AET_mean,method = "pearson") 
#print(cassava.aet)

#GDP
cassava.gdp<-perm.relation(rf.cassava$cassava_HgHa,rf.cassava$GDP_Mean,method = "pearson") 
#print(cassava.gdp)

#Pest
cassava.pest<-perm.relation(rf.cassava$cassava_HgHa,rf.cassava$Pesticide,method = "pearson") 
#print(cassava.pest)

#Fertilizer
cassava.fert<-perm.relation(rf.cassava$cassava_HgHa,rf.cassava$cassava_Fertilizer,method = "pearson")
#print(cassava.fert)

##Groundnut
rf.groundnut<-read.csv(file="Models/Groundnut_RF.csv", header = T, row.names = 1)
rf.groundnut$Growing_Mean<-as.numeric(rf.groundnut$Growing_Mean)
rf.groundnut<-na.omit(rf.groundnut)
rf.groundnut<-log10(rf.groundnut+1)

#AET
groundnut.aet<-perm.relation(rf.groundnut$groundnut_HgHa,rf.groundnut$AET_mean,method = "pearson") 
#print(groundnut.aet)

#GDP
groundnut.gdp<-perm.relation(rf.groundnut$groundnut_HgHa,rf.groundnut$GDP_Mean,method = "pearson") 
#print(groundnut.gdp)

#Pest
groundnut.pest<-perm.relation(rf.groundnut$groundnut_HgHa,rf.groundnut$Pesticide,method = "pearson") 
#print(groundnut.pest)

#Fertilizer
groundnut.fert<-perm.relation(rf.groundnut$groundnut_HgHa,rf.groundnut$groundnut_Fertilizer,method = "pearson")
#print(groundnut.fert)

##Maize
rf.maize<-read.csv(file="Models/Maize_RF.csv", header = T, row.names = 1)
rf.maize$Growing_Mean<-as.numeric(rf.maize$Growing_Mean)
rf.maize<-na.omit(rf.maize)
rf.maize<-log10(rf.maize+1)

#AET
maize.aet<-perm.relation(rf.maize$maize_HgHa,rf.maize$AET_mean,method = "pearson") 
#print(maize.aet)

#GDP
maize.gdp<-perm.relation(rf.maize$maize_HgHa,rf.maize$GDP_Mean,method = "pearson") 
#print(maize.gdp)

#Pest
maize.pest<-perm.relation(rf.maize$maize_HgHa,rf.maize$Pesticide,method = "pearson") 
#print(maize.pest)

#Fertilizer
maize.fert<-perm.relation(rf.maize$maize_HgHa,rf.maize$maize_Fertilizer,method = "pearson")
#print(maize.fert)

##Millet

rf.millet<-read.csv(file="Models/Millet_RF.csv", header = T, row.names = 1)
rf.millet$Growing_Mean<-as.numeric(rf.millet$Growing_Mean)
rf.millet<-na.omit(rf.millet)
rf.millet<-log10(rf.millet+1)

#AET
millet.aet<-perm.relation(rf.millet$millet_HgHa,rf.millet$AET_mean,method = "pearson") 
#print(millet.aet)

#GDP
millet.gdp<-perm.relation(rf.millet$millet_HgHa,rf.millet$GDP_Mean,method = "pearson") 
#print(millet.gdp)

#Pest
millet.pest<-perm.relation(rf.millet$millet_HgHa,rf.millet$Pesticide,method = "pearson") 
#print(millet.pest)

#Fertilizer
millet.fert<-perm.relation(rf.millet$millet_HgHa,rf.millet$millet_Fertilizer,method = "pearson")
#print(millet.fert)

##Rapeseed
rf.rapeseed<-read.csv(file="Models/Rapeseed_RF.csv", header = T, row.names = 1)
rf.rapeseed<-na.omit(rf.rapeseed)
rf.rapeseed<-log10(rf.rapeseed+1)

#AET
rapeseed.aet<-perm.relation(rf.rapeseed$rapeseed_HgHa,rf.rapeseed$AET_mean,method = "pearson") 
#print(rapeseed.aet)

#GDP
rapeseed.gdp<-perm.relation(rf.rapeseed$rapeseed_HgHa,rf.rapeseed$GDP_Mean,method = "pearson") 
#print(rapeseed.gdp)

#Pest
rapeseed.pest<-perm.relation(rf.rapeseed$rapeseed_HgHa,rf.rapeseed$Pesticide,method = "pearson") 
#print(rapeseed.pest)

#Fertilizer
rapeseed.fert<-perm.relation(rf.rapeseed$rapeseed_HgHa,rf.rapeseed$rapeseed_Fertilizer,method = "pearson")
#print(rapeseed.fert)

##Rice
rf.rice<-read.csv(file="Models/Rice_RF.csv", header = T, row.names = 1)
rf.rice<-na.omit(rf.rice)
rf.rice<-log10(rf.rice+1)

#AET
rice.aet<-perm.relation(rf.rice$rice_HgHa,rf.rice$AET_mean,method = "pearson") 
#print(rice.aet)

#GDP
rice.gdp<-perm.relation(rf.rice$rice_HgHa,rf.rice$GDP_Mean,method = "pearson") 
#print(rice.gdp)

#Pest
rice.pest<-perm.relation(rf.rice$rice_HgHa,rf.rice$Pesticide,method = "pearson") 
#print(rice.pest)

#Fertilizer
rice.fert<-perm.relation(rf.rice$rice_HgHa,rf.rice$rice_Fertilizer,method = "pearson")
#print(rice.fert)

##Rye
rf.rye<-read.csv(file="Models/Rye_RF.csv", header = T, row.names = 1)
rf.rye<-na.omit(rf.rye)
rf.rye<-log10(rf.rye+1)

#AET
rye.aet<-perm.relation(rf.rye$rye_HgHa,rf.rye$AET_mean,method = "pearson") 
#print(rye.aet)

#GDP
rye.gdp<-perm.relation(rf.rye$rye_HgHa,rf.rye$GDP_Mean,method = "pearson") 
#print(rye.gdp)

#Pest
rye.pest<-perm.relation(rf.rye$rye_HgHa,rf.rye$Pesticide,method = "pearson") 
#print(rye.pest)

#Fertilizer
rye.fert<-perm.relation(rf.rye$rye_HgHa,rf.rye$rye_Fertilizer,method = "pearson")
#print(rye.fert)

##Sorghum
rf.sorghum<-read.csv(file="Models/Sorghum_RF.csv", header = T, row.names = 1)
rf.sorghum<-na.omit(rf.sorghum)
rf.sorghum<-log10(rf.sorghum+1)

#AET
sorghum.aet<-perm.relation(rf.sorghum$Yield,rf.sorghum$Evapotranspiraton,method = "pearson") 
#print(sorghum.aet)

#GDP
sorghum.gdp<-perm.relation(rf.sorghum$Yield,rf.sorghum$GDP,method = "pearson") 
#print(sorghum.gdp)

#Pest
sorghum.pest<-perm.relation(rf.sorghum$Yield,rf.sorghum$Pesticide,method = "pearson") 
#print(sorghum.pest)

#Fertilizer
sorghum.fert<-perm.relation(rf.sorghum$Yield,rf.sorghum$sorghum_Fertilizer,method = "pearson")
#print(sorghum.fert)

##Soybean
rf.soybean<-read.csv(file="Models/Soybean_RF.csv", header = T, row.names = 1)
rf.soybean<-na.omit(rf.soybean)
rf.soybean<-log10(rf.soybean+1)

#AET
soybean.aet<-perm.relation(rf.soybean$soybean_HgHa,rf.soybean$AET_mean,method = "pearson") 
#print(soybean.aet)

#GDP
soybean.gdp<-perm.relation(rf.soybean$soybean_HgHa,rf.soybean$GDP_Mean,method = "pearson") 
#print(soybean.gdp)

#Pest
soybean.pest<-perm.relation(rf.soybean$soybean_HgHa,rf.soybean$Pesticide,method = "pearson") 
#print(soybean.pest)

#Fertilizer
soybean.fert<-perm.relation(rf.soybean$soybean_HgHa,rf.soybean$soybean_Fertilizer,method = "pearson")
#print(soybean.fert)

##Sunflower
rf.sunflower<-read.csv(file="Models/Sunflower_RF.csv", header = T, row.names = 1)
rf.sunflower<-na.omit(rf.sunflower)
rf.sunflower<-log10(rf.sunflower+1)

#AET
sunflower.aet<-perm.relation(rf.sunflower$sunflower_HgHa,rf.sunflower$AET_mean,method = "pearson") 
#print(sunflower.aet)

#GDP
sunflower.gdp<-perm.relation(rf.sunflower$sunflower_HgHa,rf.sunflower$GDP_Mean,method = "pearson")
#print(sunflower.gdp)

#Pest
sunflower.pest<-perm.relation(rf.sunflower$sunflower_HgHa,rf.sunflower$Pesticide,method = "pearson") 
#print(sunflower.pest)

#Fertilizer
sunflower.fert<-perm.relation(rf.sunflower$sunflower_HgHa,rf.sunflower$sunflower_Fertilizer,method = "pearson")
#print(sunflower.fert)

##Wheat
rf.wheat<-read.csv(file="Models/Wheat_RF.csv", header = T, row.names = 1)
rf.wheat<-na.omit(rf.wheat)
rf.wheat<-log10(rf.wheat+1)

#AET
wheat.aet<-perm.relation(rf.wheat$wheat_HgHa,rf.wheat$AET_mean,method = "pearson") 
#print(wheat.aet)

#GDP
wheat.gdp<-perm.relation(rf.wheat$wheat_HgHa,rf.wheat$GDP_Mean,method = "pearson") 
#print(wheat.gdp)

#Pest
wheat.pest<-perm.relation(rf.wheat$wheat_HgHa,rf.wheat$Pesticide,method = "pearson")
#print(wheat.pest)

#Fertilizer
wheat.fert<-perm.relation(rf.wheat$wheat_HgHa,rf.wheat$wheat_Fertilizer,method = "pearson")
#print(wheat.fert)

# Tabulate in Excel and then import
vard<-read.csv(file="Models/VariableDirection/VariableDirection.csv", header=T, row.names = 1)

distance<-dist(vard, method = "euclidean")
vard.hc<-hclust(distance)
plot(vard.hc) #reorder in excel 

#reimport
vard<-read.csv(file="Models/VariableDirection/VariableDirection.csv", header=T)

vard$Crop<-factor(vard$Crop, levels=vard$Crop) #set factor
vard.m<-melt(vard) #melt

#heatmap
library(reshape2)
ggplot(vard.m, aes(x=vard.m$variable, y=vard.m$Crop, fill=vard.m$value)) + 
  geom_tile() + 
  scale_fill_gradientn(colours = pal) + 
  scale_x_discrete(expand = c(0, 0)) +
  scale_y_discrete(expand = c(0, 0))  + 
  coord_equal() +xlab("Variable") +ylab("Crop")  +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+ scale_fill_viridis(option = "D") 



```


